### 2023-04-20 paper.tex
minor changes

\begin{figure*}
	\begin{center}
		\includegraphics[width=.7\textwidth]{figures/Fig_DMRs.png}
	\end{center}
	\caption{\small \textbf{Detection of differentially methylated regions between oligodendrocytes and neural stem cells.}\\
		\textbf{(A)} DMRs detected between 58 oligodendrocytes (ODs) and 130 neural stem cells (NSCs) from \citep{kremer_scnmt} (top) and DMRs detected in the same data with randomly permuted cell labels (bottom, used to estimate FDR and determine adjusted p-values).
		\textbf{(B)} Enrichment of GO terms associated with DMRs lowly methylated in ODs (top) or NSCs (bottom).
		Depicted are the top 5 GO terms of the "Biological Process" (GO:BP) and "Cellular Component" (GO:CC) GO category, and their binomial test p-value and enrichment, as reported by GREAT \citep{mclean2010great}.
		\textbf{(C)} Mean methylation of NSCs and ODs at an exemplary DMR.
		Each point corresponds to a cell, black lines denote the median.
		\textbf{(D)} Detailed view of the DMR (yellow dashed rectangle) from \textbf{C} in pseudo-bulk samples consisting of NSCs or ODs.
		Vertical bars represent CpG sites.
	}
	\label{fig:dmr}
\end{figure*}

>>>>

\begin{figure*}
	\begin{center}
		\includegraphics[width=.7\textwidth]{figures/Fig_DMRs.png}
	\end{center}
	\caption{\small \textbf{Detection of differentially methylated regions between oligodendrocytes and neural stem cells.}\\
		\textbf{(A)} DMRs detected between 58 oligodendrocytes (ODs) and 130 neural stem cells (NSCs) from \citet{kremer_scnmt} (top) and DMRs detected in the same data with randomly permuted cell labels (bottom, used to estimate FDR and determine adjusted p-values).
		\textbf{(B)} Enrichment of GO terms associated with DMRs lowly methylated in ODs (top) or NSCs (bottom).
		Depicted are the top 5 GO terms of the "Biological Process" (GO:BP) and "Cellular Component" (GO:CC) GO category, and their binomial test p-value and enrichment, as reported by GREAT \citep{mclean2010great}.
		\textbf{(C)} Mean methylation of NSCs and ODs at an exemplary DMR.
		Each point corresponds to a cell, black lines denote the median.
		\textbf{(D)} Detailed view of the DMR (yellow dashed rectangle) from C in pseudo-bulk samples consisting of NSCs or ODs.
		Vertical bars represent CpG sites.
	}
	\label{fig:dmr}
\end{figure*}
